### 2020-04-30 final_report/results.tex
improve typesetting
nicer figure 9

\begin{figure}[h]
	\centering
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{exp1_slice0}
		\caption{Run 2, batches 0-2}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{exp1_slice1}
		\caption{Run 2, batches 100-102}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{exp1_slice2}
		\caption{Run 2, batches 200-202}
	\end{subfigure}
	\caption{20~best-performing surrogates per each considered family, plotted in
		terms of complexity (as $\overline{t}_{\text{pred.}}$) and regression
		performance (as~$R^2$) on selected slices of run~2, evaluated in
	experiment~1. Here, batches refer to subsets of training and test datasets that
	may be matched to slices using~\cref{tbl:slices}.}
	\label{fig:exp1-time-vs-reg}
\end{figure}

\begin{wrapfigure}{r}{0.333\textwidth}
	\centering
	\includegraphics[width=\linewidth]{exp2_time_vs_reg}
	\caption{Results of experiment~2, plotted analogously
	to~\cref{fig:exp1-time-vs-reg}.}
	\label{fig:exp2-time-vs-reg}
\end{wrapfigure}

@@

@@

@@

\begin{wrapfigure}{r}{0.4\textwidth}
	\centering
	\includegraphics[width=0.4\textwidth]{fig5_sintoy.jpg}
	\caption{Sinusoidal toy TBR theory over two continuous parameters, wavenumber 1}
	\label{fig:sintoy}
\end{wrapfigure}

@@

An increase in MCMC candidate samples was seen to have a positive but very weak
effect on final surrogate precision, suggesting that the runtime of MCMC on each
iteration can be limited for increased efficiency. -- Awaiting test results on
initial sample quantity --. The most complex dynamics arose with the adjustment
of sample increment, shown in~\cref{fig:qassincr}. For each tested initial sample quantity N, the optimal number of step samples was seen to be well-approximated by $\sqrt{N}$; the plotted error trends suggest that incremental samples larger than this optimum give slower model improvement on both the training and evaluation sets, and a larger minimum error on the evaluation set. This performance distinction is predicted to be even more significant when trained on the expensive MC model, where the number of sample evaluations will serve as the primary bottleneck for computation time.
\begin{figure}[h!]
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=1.1\linewidth]{fig6a_qassincrsamp.pdf}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=1.1\linewidth]{fig6b_qassincrtime.pdf}
    \end{subfigure}
    \caption{QASS absolute training error over total sample quantity (left) and number of iterations (right). MAE represents surrogate error on the adaptively-sampled training/test set, and E\_MAE on the independent evaluation sets.}
    \label{fig:qassincr}
\end{figure}

@@

\begin{figure}[h]
  \centering
    \includegraphics[width=0.8\linewidth]{fig7_qasssampling.pdf}
    \caption{Absolute training error for QASS, baseline scheme, and mixed scheme}
  \label{fig:qasssampling}
\end{figure}

>>>>

\begin{figure}[h]
	\centering
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{exp1_slice0}
		\caption{Run 2, batches 0-2}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{exp1_slice1}
		\caption{Run 2, batches 100-102}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{exp1_slice2}
		\caption{Run 2, batches 200-202}
	\end{subfigure}
	\caption{20~best-performing surrogates per each considered family, plotted in
		terms of complexity (as~$\overline{t}_{\text{pred.}}$) and regression
		performance (as~$R^2$) on selected slices of run~2, evaluated in
	experiment~1. Here, batches refer to subsets of training and test datasets that
	may be matched to slices using~\cref{tbl:slices}.}
	\label{fig:exp1-time-vs-reg}
\end{figure}

@@

\begin{wrapfigure}[10]{r}{0.333\textwidth}
	\centering
	\vspace{-2ex}
	\includegraphics[width=\linewidth]{exp2_time_vs_reg}
	\caption{Results of experiment~2, plotted analogously
	to~\cref{fig:exp1-time-vs-reg}.}
	\label{fig:exp2-time-vs-reg}
\end{wrapfigure}

@@

\begin{wrapfigure}[13]{r}{0.4\textwidth}
	\centering
	\vspace{-12ex}
	\includegraphics[width=0.4\textwidth]{fig5_sintoy.jpg}
	\caption{Sinusoidal toy TBR theory over two continuous parameters, wavenumber 1}
	\label{fig:sintoy}
\end{wrapfigure}

@@

@@

An increase in MCMC candidate samples was seen to have a positive but very weak
effect on final surrogate precision, suggesting that the runtime of MCMC on each
iteration can be limited for increased efficiency. -- Awaiting test results on
initial sample quantity --. The most complex dynamics arose with the adjustment
of sample increment, shown in~\cref{fig:qassincr}. For each tested initial sample quantity N, the optimal number of step samples was seen to be well-approximated by $\sqrt{N}$; the plotted error trends suggest that incremental samples larger than this optimum give slower model improvement on both the training and evaluation sets, and a larger minimum error on the evaluation set. This performance distinction is predicted to be even more significant when trained on the expensive MC model, where the number of sample evaluations will serve as the primary bottleneck for computation time.
\begin{figure}[h!]
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=1.1\linewidth]{fig6a_qassincrsamp.pdf}
    \end{subfigure}%
    \hfill
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=1.1\linewidth]{fig6b_qassincrtime.pdf}
    \end{subfigure}
    \caption{QASS absolute training error over total sample quantity (left) and number of iterations (right). MAE represents surrogate error on the adaptively-sampled training/test set, and E\_MAE on the independent evaluation sets.}
    \label{fig:qassincr}
\end{figure}

@@

\begin{figure}[h]
  \centering
    \includegraphics[width=0.78\linewidth]{fig7_qasssampling.pdf}
    \caption{Absolute training error for QASS, baseline scheme, and mixed scheme}
  \label{fig:qasssampling}
\end{figure}
